---
title: "a2munge User Guide"
author: "Haarstick"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a2munge User Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Overview

a2munge is an R package to help create _Big Data_ Advanced Analytic data pipelines. The package contains a suite of Spark^[Spark Data Processing Engine[via](https://spark.apache.org/)] compatible data preparation, transformation and analytic functions (aka munging). Advanced Analytics data pipelines, or data pipelines to create statistical model training data often require complex data cleansing, transformation and preperation. The a2munge package is design to efficiently create such pipelines. 
 
 
### Features

* Data transformation functions support Spark and in-memory R data set classes 
* Functions are compatible with dplyr^[dplyr R package [via](https://dplyr.tidyverse.org/)] and tidyr^[tidyr R package [via](https://tidyr.tidyverse.org/)] verbs
* Individual functions can be combined to create flexible, complex data pipelines
* Programmatic function interface support application and solution templates
* Combines with a2modeler R package to allow Advanced Analytics application development to be done with a single programming language (vs traditional sql / statistical software split) 
* Statistical Anomaly Detection for time series data
 

### Design

a2munge leverages the R S3^[R S3 OO [via](http://adv-r.had.co.nz/S3.html)] Object Oriented system to create generic functions with R data.frame and Spark class methods. This design creates a similiar set of functions and arguments for the user that can be applied on local R data.frames, local Spark data objects, or even distributed Spark objects. 


a2munge uses standard evaluation ^[dplyr standard evaluation intro [via](https://dplyr.tidyverse.org/articles/programming.html)] to evaluate function arguments. This allows for function arguments to be assigned programmatically which is beneficial for re-usable template and component development. 


a2munge functions standarize the output naming convention and schema which creates consistency aiding in application development.


a2munge spark compatibility relies on the great sparklyr^[sparklyr R package [via](https://spark.rstudio.com/)] R package which enables a R API for working with Spark objets. 


## Functions

In the following sections each of the a2munge functions are explained with examples. In the chunk below an sample dataset is create in local R. A local Spark connection is created and the sample dataset is copied to the Spark environment. 


```{r, message=FALSE, warning=FALSE}

# R packages
library(tidyverse)
library(lubridate)
library(sparklyr)

# Create Simulated Dataset:
set.seed(319)
n <- 100                           # Records per ID
id_vars <- seq(101, 200, by=1)     # Unique IDs
dates <- today() - days(1:90)      # Date Range
cat1 <- LETTERS[1:2]               # Category Var 1
cat2 <- LETTERS[c(22:26)]          # Category Var 2

df <- tibble()
for(id in id_vars){
  d <- tibble(id = id,
              date = as.character(sample(dates, n, replace = T)),
              cat1 = sample(cat1, n, replace = T, prob = c(.75, .25)),
              cat2 = sample(cat2, n, replace = T, prob = c(.4, .3, .2, .075, .025)),
              metric1 = sample(1:5, n, replace = T),
              metric2 = rnorm(n, mean=50, sd = 5))
  df <- rbind(df, d)
}


# Create Spark Connection
sc <- spark_connect(master = "local")

# Copy Data to Spark
sdf <- copy_to(sc, df, "df", overwrite = TRUE)
```


```{r}
# R Dataset
df

# Spark Dataset
sdf
```


### Manipulaters

The first set of functions are data manipulater: functions to aggregate or add new columns as functions of other columns

#### Summariser

The summariser function 


#### Summariser Map


#### Mutater


#### Roller


#### Lagger


#### Imputer




### Reshapers

#### Pivoter


#### Melter


#### Expander




### Time Series


#### Indexer


#### Date Parter


#### Collapser


#### Formatter


#### Converter




### Others


#### Reader


#### Writer


#### Sampler


#### Collecter